My title

### 2024-02-12 paper/paper.qmd
Finished simulating and testing the data

# Filtering the data to only include Harris County
reasons_data_harris <- reasons_data_cleaned |>
  filter(county == "HARRIS")
```

@@

>>>>

# Loading the Harris County data
reasons_data_harris <- read_csv(here::here("data/replication/reasons_data_harris.csv"))
```

@@

# Sketches {#sec-sketches}

Sketches of the data and graphs are available in the GitHub Repository associated with this report.

# Simulation {#sec-simulation}

A script containing data simulation is available in the GitHub Repository associated with this report. This script was generated using the R programming language [@citeR] and the `janitor` [@citejanitor] and `tidyverse` [@citetidyverse] packages.

# Tests {#sec-tests}

The simulated and actual data were tested using the R programming language [@citeR] and the `tidyverse` [@citetidyverse] package. Scripts containing the testing code are available in the GitHub Repository associated with this report.
